Breanna_Code

### 2022-09-29 Draft_Report.Rmd
Some text

## Load packages
I try and load packages separately from data.

@@

## view raw data
Note that the raw data contain characters that will make things tricky later on.  I would exclude parenth etc as general practice. Also names are quite long, making it difficult to include in the models.  This is where having a data dicitonary is useful, as you can keep descriptions, formal names, plot names available for use in figures.

@@

## Checking distributional assumptions
Here we would put put some text describing the results, and setting up the next section, in case there were transformations we wanted to do.

@@

### Distance
Definitely some trends with distance,  but also definitely some non-linear things happening

@@

## modeling section
```{r models}
# Example model
library(lme4)
trialmodel=glmer(`Total Abundance (ind/0.1m²)` ~ DiffuserDirection + DiffuserDistance + DiffuserDirection:DiffuserDistance + (1|Station), data = Metrics, family = poisson)

@@

>>>>

## Load packages

I try and load packages separately from data.

@@

## view raw data

Note that the raw data contain characters that will make things tricky later on. I would exclude parenth etc as general practice. Also names are quite long, making it difficult to include in the models. This is where having a data dicitonary is useful, as you can keep descriptions, formal names, plot names available for use in figures.

@@

## Checking distributional assumptions

Here we would put put some text describing the results, and setting up the next section, in case there were transformations we wanted to do.

@@

### Distance

Definitely some trends with distance, but also definitely some non-linear things happening

@@

## modeling section

```{r models}
# Example model
library(lme4)
trialmodel=glmer(`Total Abundance (ind/0.1m²)` ~ DiffuserDirection + DiffuserDistance + DiffuserDirection:DiffuserDistance + (1|Station), data = Metrics, family = poisson)

@@

Some text here
